---  
title: "Downwash impacts"  
author: "aerscreen"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: true
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Downwash impacts}
  \usepackage[utf8]{inputenc} 
---
  
<style>
  body {
    max-width: 1000px;
    margin: auto;
    padding: 1em;
    line-height: 20px ; 
  }
</style>
  
> ## Compare air dispersion results for a facility:  
> 1) Without buildings
> 2) With buildings


# Setup

## Install AERSCREEN and supporting models to _EPA_ folder
```{r eval = F}
library(installEPA)
install_epa(c("aerscreen", "bpip", "aermod", "makemet"), dir = "EPA", add_model_folder = FALSE)

# Copy aermod.exe into AERSCREEN folder
#install_dir <- paste0(getwd(), '/EPA')

#relocate <- paste0(substring(getwd(), 1, 2), " & CD ", install_dir)

#shell(paste0(relocate, '/', list.files(install_dir)[grepl("aermod", list.files(install_dir))][1], ' & COPY "', "aermod.exe", '" "', install_dir, '/aermod.exe"'))
  
```

## Create new aerscreen table
```{r eval = T}
library(aerscreen)
aer_inp <- new_aerscreen()

library(knitr)
kable(aer_inp)
```

## Assign source parameters
```{r eval = T, warning=F, message=F}
library(dplyr)

aer_inp <- mutate(aer_inp,
                  emit_gs       = 1,      # Average emissions in  grams/second
                  height_m      = 9,      # Stack height in meters
                  temp_k        = 300,    # Exit temperature in Kelvin
                  velocity_ms   = 10,     # Exit velocity in meters/second
                  diameter_m    = 1,      # Inner stack diameter in meters
                  urban_pop     = 400000) # Population of surrounding urban area

```


## Set modeling distance
```{r eval = T}
aer_inp <- mutate(aer_inp,
                  near_receptor   = 1,     # Distance from source to nearest modeling receptor in meters
                  far_receptor    = 400)   # Distance to furthest modeling receptor in meters

```


## Set surface characteristics for modeling domain
```{r eval = T}
aer_inp <- mutate(aer_inp,
                  surface_profile  = 7,    # Urban area
                  climate_profile  = 1)    # Average moisture conditions
```


# No building dispersion


## Write aerscreen input file
```{r eval = T}
write_aerscreen(aer_inp, "EPA/no_builds.inp", out_file = "no_builds.out")
```


## Run aerscreen on input file
```{r eval = T, cache =F}
no_build_results <- run_aerscreen("EPA/no_builds.inp", 
                                  out_file   = "no_build_results",
                                  exe_folder = "EPA")
```

## View results as data frame
```{r eval = T}
no_build_results <- read_aerscreen_out("no_build_results.out")

kable(no_build_results)

```


<br/>  

# With building dispersion

## Create new input file 
```{r eval = T}
# Load input file
build_inp <- read_aerscreen_inp("EPA/no_builds.inp")
```

## Assign building parameters
```{r eval = T}

# Set dimensions
new_build <- tibble::tibble(bld_height          = 16,
                            short_side          = 8,
                            long_side           = 14,
                            bld_rotation        = 15,
                            dist_from_source    = 8,
                            angle_from_source   = 10)


```

## Add building to input file
```{r eval = T}

build_inp[ , names(new_build)] <- new_build[1, ]

# Turn downwash processing on
build_inp$bpip_run <- "Y"

kable(build_inp)
```

## Run AERSCREEN on building input file
```{r eval = T, cache=F}
## Write building input file
write_aerscreen(build_inp, "EPA/builds.inp", out_file = "build_results")

## Run aerscreen on input file
build_results <- run_aerscreen("EPA/builds.inp", 
                               out_file   = "build_results",
                               exe_folder = "EPA")

## Load results as data frame
build_results <- read_aerscreen_out("build_results.out")

kable(build_results)
```


# Dispersion comparison

## Maximum concentration
```{r eval = T, fig.width = 6, fig.height = 3.5, cache =F}
library(ggplot2)
build_results$model <- "with buildings"

no_build_results$model <- "no buildings"


ggplot(rbind(build_results, no_build_results), aes(model, max_1hr_conc, fill = model)) +
  geom_bar(stat = "identity") + labs(title = "Max 1-hour")

```
