---
title: "Update simple air screening dispersion factors for risk screening"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Updating air screening dispersion factors for facilities}
---


## Objective

The default dispersion factors used for screening purposes are updated after the release of a new version of AERMOD or update to AERSCREEN. The model version `16216r` ^[AERMOD version: 16216r] was used for the current dispersion factors. The generated dispersion factors are designed to be protective and to overestimate dispersion during most real-world operating conditions. The conservative assumptions allow the results to be generalized to a wide set of operating scenarios and provide quick estimates of air concentrations for screening purposes.


## Updates  

The dispersion factors we're modeled with the adjusted U* setting on and off.

_For general questions, contact [air.modeling@mn.state.us](emailto::air.modeling@mn.state.us)._

## Assumptions

1. __Downwash:__ Worst-case downwash parameters were captured by including buildings located 0, 30 and 50 meters from the facility in each of the 8 cardinal directions. Three building heights were modeled for each scenario: 50%, 75% and 100% of the stack height.   
1. __Stack temperature:__ The minimum stack temperature was set to ambient conditions.  
1. __Exit velocity:__     The minimum exit velocity was set to 0.5 m/s.  
1. __Meteorology:__       Each scenario was modeled with default AERCREEN meteorology.

  
_The screening dispersion factors are not considered protective for facilities with exit temperatures below ambient or for sources with near zero exit velocity._
  
5. __Flat terrain:__ The model was run with the `flat terrain` option.
5. __Rural:__        The model was run with the default `rural` option.
5. __U*:__           Each scenario was modeled with adjusted U* and without.


## Alernatives

AERSCREEN uses a factor to estimate annual average concentrations - divide the 1-hour maximum by ten. While this method is appropriate for nearby receptors, the results tend to be overly protecive for distances greater than 50 meters.


## Input files

An input file was created for each of the scenario combinations below.  

  - 42 stack heights: [1 to 37 and 40, 45, 50, 60, 70] meters    
  - 6 stack diameters: [0.15, 0.3, 0.6, 1, 1.5, 3] meters    
  - 6 exit velocities: [0.5, 1, 3, 10, 20, 35] m/s  
  - 4 exit temperatures: [Ambient, 293, 315, 450] kelvin
  - 2 surface conditions: Forested and urban
  - 3 building distances
  - 3 building heights
  - 2 U-star options: U* on/off
 
## Set input parameters
```{r eval=F}
boundary_distances <- c(seq(2, 18, 2), seq(20, 120, 5), seq(125, 225, 10), seq(240, 760, 20), seq(800, 1200, 40), seq(1250, 3000, 50), seq(3200, 5000, 150))

sk_heights   <- c(1:37, 40, 45, 50, 60, 70)
  
sk_diameters <- c(0.15, 0.3, 0.6, 1, 1.5, 3) 
  
sk_velocity  <- c(0.5, 1, 3, 10, 20, 35) 

tempsK <- c(0, 293, 315, 450)

tempsF <- list("Ambient", 68, 107, 350)

surf_options <- c(2, 7)
  
u_star <- c(T, F)

build_distance <- seq(0, 30, 50)

build_ht_frx   <- seq(0.5, 0.75, 1)

n_scenarios <- length(u_star) * 
               length(sk_diameters) * 
               length(sk_velocity) * 
               length(tempsK) * 
               length(sk_heights) * 
               length(surf_options) *
               length(build_distance) *
               length(build_ht_frx)
  
```

`r paste0("A total of ", n_scenarios, " scenarios were modeled in total."`


## Install software
```{r eval = F}
##Install AERSCREEN and supporting models to _EPA_ folder
library(installEPA)
install_epa(c("aerscreen", "bpip", "aermod", "makemet"), dir = "EPA", add_model_folder = FALSE)
```


## Create blank default dispersion table
```{r eval = T}
library(dplyr)
library(knitr)

disp_table <- data_frame(stack_height      =  rep(sk_heights, each = length(boundary_distances)),
                         boundary_distance =  rep(boundary_distances, length(sk_heights)),
                         disp_1hr          = NA,
                         disp_annual       = NA)

kable(head(disp_table))
```  


## Create new aerscreen table
```{r eval = T}
library(aerscreen)
aer_inp <- new_aerscreen()


kable(aer_inp)
```  


# Set building parameters
```{r eval=T}
# Dimensions
new_build <- tibble::tibble(bld_height          = 16,
                            short_side          = 8,
                            long_side           = 14,
                            bld_rotation        = 15,
                            dist_from_source    = 8,
                            angle_from_source   = 90)
```


## Run AERMOD for each scenario
```{r eval=F}

# Set default scenario
height     = sk_heights[1]
diam       = sk_diameters[1]
velocity   = sk_velocity[1]
tempk      = tempsK[1]
star       = u_star[1]
surface    = surf_options[1]
bld_dist   = build_distance[1]
bld_ht_frx = build_ht_frx[1]

count <- 1

for(star in u_star) {
  
for(surface in surf_options) {
 
for(bld_dist in build_distance) {

for(bld_ht_frx in build_ht_frx) {
   
## Assign default parameters
aer_inp <- mutate(aer_inp,
                  emit_gs       = 1,             # Average emissions in  grams/second
                  height_m      = height,        # Stack height in meters
                  temp_k        = tempk,         # Exit temperature in Kelvin
                  velocity_ms   = velocity,      # Exit velocity in meters/second
                  diameter_m    = diam,          # Inner stack diameter in meters
                  urban_pop     = 0)             # Population of surrounding urban area
 

## Set modeling distance
aer_inp <- mutate(aer_inp,
                  near_receptor   = 1,       # Distance from source to nearest modeling receptor in meters
                  far_receptor    = 10000)   # Distance to furthest modeling receptor in meters 


## Set surface characteristics
aer_inp <- mutate(aer_inp,
                  surface_profile  = surface,    # Forest, swamp, or urban land
                  climate_profile  = 1,          # Average moisture conditions
                  adjust_ustar     = ifelse(star, "Y", "N")) 

## Add building to input file
new_build$bld_height       <- height * bld_ht_frx
new_build$dist_from_source <- bld_dist

aer_inp[ , names(new_build)] <- new_build[1, ]

# Turn downwash processing on
aer_inp$bpip_run <- "Y"


## Write AERSCREEN input file
write_aerscreen(aer_inp, "EPA/screen.inp", out_file = "screen_results")

## Run aerscreen on input file
screen_results <- run_aerscreen("EPA/screen.inp", 
                                out_file   = "screen_results",
                                exe_folder = "EPA")

for(height in sk_heights) {

for(diam in sk_diameters) {

for(velocity in sk_velocity) {

for(tempK in tempsK) {
  
  
# Print iteration count
print(count)
  
count <- count + 1

## Update source parameters
aer_inp <- mutate(aer_inp,           
                  height_m      = height,        # Stack height in meters
                  temp_k        = tempk,         # Exit temperature in Kelvin
                  velocity_ms   = velocity,      # Exit velocity in meters/second
                  diameter_m    = diam)          # Inner stack diameter in meters


## Update AERMOD input file
aermod_inp     <- readLines("EPA/screen_results.inp")


## Run AERMOD on input file
screen_results <- run_aerscreen("EPA/screen.inp", 
                                out_file   = "screen_results",
                                exe_folder = "EPA")

## Load results as data frame
screen_results <- read_aerscreen_out("EPA/screen_results.out")


## Find maximum dispersion within each 1 meter radii
for(i in 1:nrow(disp_table)) {
  
  screen <- filter(screen_results, distance > disp_table[i, ]$distance)
  
  disp_table[i, ]$disp_1hr    <- max(disp_table[i, ]$disp_1hr, 
                                     screen$max_1hr_conc, na.rm = T)
  
  disp_table[i, ]$disp_annual <- max(disp_table[i, ]$disp_annual , 
                                     screen$max_annual_conc, na.rm = T)
}

}}}}}}}}
```

 
## Results 

The tables and charts below compare the previous screening dispersion factors to the updated results. 
```{r eval=F}


```

`r 'In his later books'`

